---
title: "Data Products Assignment"
author: "Marcelo Nardelli"
date: "24/02/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a slidify presentation for the "Developing Data Products" assignment on week 4. It makes reference to a shiny application developed as part of the assignment. This application user a dataset of airbnb listings in the city of New York and shows two example plots that can be generated using this data. The application can be accessed at https://ganzah.shinyapps.io/DataProductsAssigment/ . Source code for the app and this presentation can be found on github, at https://github.com/ganzah/DataProductsWeek4

The airbnb dataset is loaded, preprocessed (NA's are replaced by zeros, listings with outlier prices are removed and only certain columns are select) and two plots are presented: a boxplot of listings prices by neighbourhood group and a boxplot of prices by neighbourhood group and room type.

## Data loading and preprocessing

```{r, warning=FALSE, message=FALSE, size=5, echo=TRUE, out.width=5}
library(dplyr); library(ggplot2); library(gridExtra); set.seed(20200224)
data <- read.csv("AB_NYC_2019.csv")
data <- data %>% as_tibble() %>%
    select(neighbourhood, neighbourhood_group, room_type, price, number_of_reviews, reviews_per_month) %>% 
    replace(., is.na(.), 0) %>% filter(price > 0) %>% filter(price <= quantile(data$price, .9))
glimpse(data)
head(data)
```

## Boxplot of listings prices by neighbourhood group

```{r cars, echo = TRUE}
newData <- data %>% filter(neighbourhood_group %in% c("Bronx", "Brooklyn", "Manhattan", "Queens", "Staten Island"))
plot1 <- ggplot(data = newData, aes(x = neighbourhood_group, y = price, fill=neighbourhood_group)) + 
  geom_boxplot() + 
  labs(title = "Prices by Neighbourhood groups", x = "Neighbourhood groups", y = "Price")
plot2 <- ggplot(newData, aes(x = room_type, y = price, fill=neighbourhood_group)) + geom_boxplot() +
  labs(title = "Prices by Neighbourhood groups and Room types", x = "Room types", y = "Price")
grid.arrange(plot1, plot2)
```

## Conclusion

The app shows some basic visualizations that can be achieved using the dataset. It showcases both reactive and non-reactive outputs. It also performs preprocessing that results in a dataset that could be used for other purposes (predicting prices, for example)

